%------------------------
% Entry-level Cover-letter Template in LaTeX
% Made to go with &quot;Entry-level Resume in laTeX&quot; - here
% Version - v1.0
% Last Edits - October 5, 2021
% Author : Jayesh Sanwal
% Reach out to me on LinkedIn(/in/jsanwal), with any suggestions, ideas, issues, etc.
%------------------------


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING 
%%%%%%% --------------------------------------------------------------------------------------

%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
% \usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=3cm]{geometry}

%%%% Set Fonts
% \setmainfont[
% BoldFont=SourceSansPro-Semibold.otf,
% ItalicFont=SourceSansPro-RegularIt.otf
% ]{SourceSansPro-Regular.otf}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}
% \rfoot{{\color{HF_color} \thepage \ of \ 1, Updated \today}}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF &quot;DO NOT TOUCH&quot; REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    
\centering
{\Huge David Dietrich} \\ %
\vspace{0.1cm}
{\color{UI_blue} \Large{\textbf{TITLE} Software Developer}} \\
\vspace{0.1cm}
\large david.drich@gmail.com 
$\vert$
\large {\href{https://www.linkedin.com/in/david-drich/}{linkedin.com/in/david-drich} }

\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.2cm}
\begin{center}
    {\color{UI_blue} \Large{COVER LETTER}}
\end{center}


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------

Date: \today \par \vspace{-0.1cm}
Dear Hiring Manager, % OR To whom this may concern, 

\textbf{REMOVE BEFORE SENDING: Make minor changes as needed to tailor to company.}

I am excited to apply for the role of \textbf{ROLE} with \textbf{COMPANY}. As a highly motivated and results-driven developer, I believe that my skills and experience align perfectly with the requirements of this position. \par

During my tenure at Google I have worked on cross-functional teams across mobile, backend, and cloud organizations. My work in Android Google Maps saw me solving complex technical problems to deliver significant improvements to developer productivity and pay down tech debt that had been accumulating for a decade. I also became intimately familiar with almost all aspects of test and release pipelines in order to optimize those processes. More recently, my work in Google Cloud led to my designing the cloud infrastructure and release process for a new Cloud product using Kubernetes. During that work, I extensively used Terraform and Kubectl to design the cluster for whatever requirements were needed. \par

I am highly motivated by complex technical challenges, improving developer productivity, and making an excellent product for the end user. Not only my interests, but also my practical experience, I believe make me an excellent fit for this role in \textbf{ORG}. \par

I look forward to speaking with you about how I can put my skills to use for your organization. Thank you for considering my application. \par

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  Signature
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Sincerely, \\
\vspace{0.2cm}
\raggedright
David Dietrich \\ david.drich@gmail.com

\end{document}

