% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008-2015 Nathaniel Johnston <nathaniel@njohnston.ca> http://www.njohnston.ca
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{enumitem}
\usepackage{hyperref}
\urlstyle{same}

% The following two lines are needed to fix a MacTex compatibility issue
% Thanks to Tony Blake for finding this fix!
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{0pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{1}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{-5pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-10pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\ressubheadinglong}[8]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & #4 \\
		\textit{#5} & #6 \\
		\textit{#7} & #8 \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
	\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
\newcommand\rurl[1]{%
	\href{http://www.#1}{\nolinkurl{#1}}%
}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\huge David Dietrich} & \textbf{March 2023} \\
	Software Developer & david.drich@gmail.com \\
	Waterloo, Ontario & \rurl{linkedin.com/in/david-drich} \\
\end{tabular*}
\\

\vspace{5pt}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Objective}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{center}
	  \parbox{6.762in}{Self-directed learner seeking a Software Developer position in a fast-paced and challenging environment. Thrives in ambiguity. Proven tech lead. 10+ years of experience. Strong collaboration skills and several years of experience mentoring junior developers.}
  \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}[leftmargin=*]
\item[]
	\ressubheading{Google}{USA/Japan/Canada}{Software Engineer - Google Cloud}{Jan 2022 - April 2023}
	\begin{itemize}
		\resitem{Designed and built Terraform and Kubernetes configurations, release pipeline, and probers for single-tenant GKE clusters.}
		\resitem{Drove decision to migrate Cloud source-control product from GCP VMs to GKE, reducing the work required for the eventual public release by 3+ eng months.}
	\end{itemize}
	\ressubsubheading{Software Engineer - Android Platform}{Mar 2020 - Jan 2022}
	\begin{itemize}
		\resitem{Created new configuration system and migrated existing test definitions, resulting in an over 10x reduction in test definition LOC.}
		\resitem{Designed and built performance testing suite for Android platform modules, catching performance regressions much earlier in the development lifecycle.}
	\end{itemize}
	\ressubsubheading{Software Engineer, Tools and Infrastructure - Android Google Maps}{Jan 2014 - Mar 2020}
	\begin{itemize}
		\resitem{Lead team tasked with improving developer velocity. We significantly improved test flakiness and test performance, reducing wall time of code submissions from 45 minutes to 25 minutes. Resulting in 6+ eng-months of waiting time saved per year.}
		\resitem{Refactored build configurations for Android Google Maps to improve readability and build performance, reducing average wall time of incremental builds by approximately 5 minutes.}
		\resitem{Designed and built conformance test infrastructure and test suite for Android Auto. This suite is shipped to OEMs for verification of their Android Auto implementation in vehicles.}
	\end{itemize}

\item[]
	\ressubheading{University of Waterloo}{Waterloo, ON}{Research Assistant: Formal Methods Lab}{Sept 2011 - May 2013}
	\ifdefined\longresume
		\begin{itemize}
			\resitem{Created and extended modelling languages and model verification tooling in an automotive context.}
			\resitem{Performed research presentations for industrial partners and visiting researchers.}
		\end{itemize}
	\fi

\item[]
	\ressubheading{University of Alberta}{Edmonton, AB}{Web Developer}{May 2011 - Sept 2011}
	\ifdefined\longresume
		\begin{itemize}
			\resitem{Created web-based info system for storing, editing, and searching faculty profiles at the University of Alberta using PHP, HTML, and JS.}
		\end{itemize}
	\fi

\item[]
	\ressubheading{Energy Navigator Inc.}{Calgary, AB}{Junior Software Developer}{May 2009 - Aug 2010}
	\ifdefined\longresume
		\begin{itemize}
			\resitem{Code and tooling for AFE Navigator, an expenditure tracking platform for energy companies.}
			\resitem{Primarily worked in C\#. Additionally, some VB.NET, Java, and PL/SQL.}
		\end{itemize}
	\fi

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}[leftmargin=*]
\item[]
	\ressubheading{University of Waterloo}{Waterloo, ON}{M.Math Computer Science}{2011 - 2013}
	\ifdefined\longresume
		\begin{itemize}
			\resitem{Thesis Topic: A Mode-Based Behaviour Pattern for Feature Requirements, and a Generic Feature Interface}
			\resitem{GPA: \textbf{89/100}}
			\resitem{List out publications if they fit...}
		\end{itemize}
	\fi

\item[]
	\ressubheading{University of Alberta}{Edmonton, AB}{B.Sc. Computer Science}{2006 - 2011}
	\ifdefined\longresume
		\begin{itemize}
			\resitem{GPA: \textbf{3.6/4.0}}
		\end{itemize}
	\fi
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Technical Skills}
% I should adjust these as needed for each role.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}[leftmargin=*, itemsep=-5pt]
\item[]
	\textbf{Frameworks:} Bazel, Kubernetes, GCP, Terraform, Git, Jenkins, Cloud Build, Protobuf, Linux, Git
\item[]
	\textbf{Languages:} Python, Java, GCL, Bash
\end{itemize}

\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
	 & \textit{References available upon request} \\
\end{tabular*}\vspace{-6pt}

\end{document}
